---
title: "Data 612 Pin Tzu Lin "
author: "Lin Pin Tzu (Ruby)"
date: "2/24/2022"
output: pdf_document
---
library(tidyverse)
library(dplyr)
library(ggplot2)

#1 Using the midwest data frame produce a data table that shows output for the 
# IL only.  Produce correct output by using two methods. First use
# the piping method and then use the assignment method.
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
###piping method

midwest %>%
  filter(state == "OH")
  midwest %>%
  filter(state == "Il")

###Assignmet method
Il <-filter(midwest,state == "Il")
print(Il)
```
#2 Using the midwest data frame, produce a data table that shows 
# white population that is greater than 50,000 but less than 90,000 for 
# the state of Indiana (IN)
```{r}
IN <- midwest %>%
  select(state,popwhite) %>%
  filter(state == "IL" , popwhite >= 50000 & popwhite<= 90000)
IN
```
#3
# Using the midwest data , produce a data frame (20 observations)
# that shows only the variables state, county, poptotal , 
# popamerindian, percamerindian for the state of Indiana.  Also your data
# frame should show popamerindian in descending order.
# Which county in Indiana has the highest number of Native Americans?
```{r}
IN20 <-midwest %>%
  select(state,county,poptotal,popamerindian,percamerindan) %>%
  filter(state == "IL")
  IN20
IN20 <-  arrange(IN20,desc(popamerindian))
head(IN20,20)
# Which county in Indiana has the highest number of Native Americans? Martion county 
```
#4
# Using the midwest data and dplyr functions, create a data frame for
# only the state of Michigan (MI) showing those counties that have a 
# known poverty population that is greater than 10,000 and a percentage 
# of professionals that is greater than 10 percent. Only select variables
# that you need for the data frame, Your output should only have four
# variables and six (rows) / observations.
```{r}
MI <-midwest %>%
  select(state,county,poppovertyknown,percprof) %>%
  filter(state == "MI",poppovertyknown > 10000 & midwest$percprof > 10) 
  MI
```
#5  
# Using the midwest data and dplyr commands and functions, write r code
# that will show the mean of the poverty population for the counties of each state.
```{r}
 midwest5 <- midwest %>% 
           group_by(state) %>%
           summarize(poppovertyknown = mean(poppovertyknown)) %>%
           select(state, poppovertyknown)
 midwest5

```
#6 
# Using the midwest data, produce a scatter plot showing a relationship
# between the variables  poppovertyknown and poptotal (Let poptotal = x and 
# poppovertyknown = y).
```{r}
ggplot(midwest,mapping = aes(x=poptotal,y= poppovertyknown))+
  geom_point()+
  labs(title = "A relationship poptotal vs poppovertyknown")+
  theme_bw()
```
#7 
# Using the midwest data, write r code that will produce the following
# side by side boxplots.
```{r}
ggplot(data = midwest, mapping = aes(x = state, y = percadultpoverty)) +
  geom_boxplot()
```
#8
# Using the midwest data, write r code that will produce a facet plot
# that shows scatter plots (red data points) with respect to the levels
# for the variable state. Also add code that will generate regression
# lines through your scatter plots that feature x = percollege and y = percprof.
# Title your facet plot "College/Professional Work Scatter Plots"
```{r}
ggplot(midwest,mapping = aes(x=percollege,y=percprof,fill=state))+
  geom_point(color="red")+
  geom_smooth(method = lm)+
  facet_wrap(~state, ncol = 3)+
  labs(title = "College/Professional Work Scatter Plots")
```
#9
# Using the midwest data frame, create a bar graph that shows the 
# different counts for each state in the data set. Your bars should
# have different colors.  Which state has the highest count?
```{r}
ggplot(midwest, aes(x = state,fill=state)) +
  geom_bar() 
# Which state has the highest count?  Illinois(IL)has the highest counts
```
#10
# The formula used to find the volume of a cylinder is 
# V = pi times r squared and the formula to find the Surface Area
# of a cylinder is A = 2(pi times r times h + pi times r squared)
# Using the formal notation and process for writing a function, as
# demonstrated in class, to write a function that will calculate the 
# Volume and the Surface Area of a given cylinder. Test your function
# by calculating answers for r = 5 and h = 10.
```{r}
#### Volume of a given cylinder
cylinderV <- function(pi,r,h){
  V <- pi*r^2*h
  return(V)
}
cylinderV(pi,5,10)
####Surface Area of a given cylinder
cylinderSA <- function(pi,r,h){
  SA=2*(pi*(r*h)+pi*r^2)
  return(SA)
}
cylinderSA(pi,5,10)
```
#11
# A partial data frame to be generated from the midwest data frame is
# given below. Write r code and apply dplyr functions that will produce 
# an additional 20 rows to the 5 rows shown.
```{r}
library(tidyverse)
  midwest %>%
           mutate(state = recode(state, WI = "Wisconsin")) -> midwest_wi1
         
         midwestWI <- midwest_wi1 %>%
           mutate(Ratio = popadults/poptotal, percent = (popadults/poptotal)*100) %>%
           filter(state == "Wisconsin") %>%
           select(state, county, poptotal, popadults, Ratio, percent)
         head(midwestWI,25)
```
#12
#Use ggplot coding to produce the side by side plots shown below. (Hint: use the categorical variable state and the quantitative variable area of the midwest data table.
```{r}
 ggplot(midwest,mapping = aes(x=area,y= state,fill=state))+
    geom_violin()+
    labs(title = "Viollin plots(area vs state)")
```
